Temporal consistency in Video NL-Bayes

### 2016-07-20 doc/201504_acivs/paper.tex

\begin{table}[htp!]
	\begin{center}
	\renewcommand{\tabcolsep}{3mm}
	\renewcommand{\arraystretch}{1.0}
	\begin{tabular}{ c | l |c c c c}
		\hline
		\rule{0pt}{12pt}$\sigma$ & Method     & Tennis       & Coastguard   & Foreman      & Bus          \\\hline
		\multirow{5}{*}{$10$} & V-BM4D \cite{Maggioni2012}       & \best{36.42} & \best{37.27} &       37.92  &       36.23  \\
		                      & V-BM4D-np     &       35.56  &       36.20  &       36.90  &       35.09  \\
		                      & V-BM3D        &       36.04  &       36.82  &       37.52  &       34.96  \\
		                      & VNLB $n_t = 0$ &       34.43  &       36.70  &       37.21  &       35.58  \\
		                      & VNLB $n_t = 3$ &       35.04  &       37.19  &       37.88  &       36.19  \\
									 & VNLB $n_t = 5$ &       35.28  & \best{37.30} & \best{38.11} & \best{36.37} \\\hline
%									 
		\multirow{5}{*}{$20$} & V-BM4D  \cite{Maggioni2012}       & \best{32.88} & \best{33.61} & \best{34.62} &       32.27  \\
		                      & V-BM4D-np     &       31.67  &       32.24  &       33.34  &       30.95  \\
		                      & V-BM3D        &       32.54  &       33.39  &       34.49  &       31.03  \\
		                      & VNLB $n_t = 0$ &       30.65  &       32.70  &       33.64  &       31.39  \\
									 & VNLB $n_t = 3$ &       31.26  &       33.35  &       34.25  &       32.11  \\
									 & VNLB $n_t = 5$ &       31.49  &       33.55  &       34.45  & \best{32.35} \\\hline
%									 
		\multirow{5}{*}{$40$} & V-BM4D   \cite{Maggioni2012}      & \best{29.52} & \best{30.00} & \best{31.30} &       28.32  \\
		                      & V-BM4D-np     &       27.97  &       28.43  &       29.69  &       27.02  \\
		                      & V-BM3D        &       29.20  &       29.99  &       31.17  &       27.34  \\
		                      & VNLB $n_t = 0$ &       27.43  &       28.88  &       30.15  &       27.60  \\
									 & VNLB $n_t = 3$ &       27.97  &       29.60  &       30.72  &       28.23  \\
									 & VNLB $n_t = 5$ &       28.11  &       29.78  &       30.82  & \best{28.40} \\\hline
	\end{tabular}
	\end{center}
	\caption{PSNRs obtained for the four classic color test sequences reported in
	\cite{Maggioni2012}. See text for details.}
	\label{tab:psnr}
\end{table}

\begin{table}[htp!]
	\begin{center}
	\renewcommand{\tabcolsep}{2mm}
	\renewcommand{\arraystretch}{1.0}
	\begin{tabular}{ c | l |c c c c c}
		\hline
		\rule{0pt}{12pt}$\sigma$ & Method     & Army & DogDance & Evergreen & Mequon & Walking  \\\hline
		\multirow{5}{*}{$10$} & V-BM4D-np      &       37.77  &       35.70  &       35.40  &       38.09  &       38.85  \\
		                      & VNLB $n_t = 0$ &       36.90  &       35.42  &       34.84  &       38.43  &       38.86  \\
		                      & VNLB $n_t = 3$ &       37.65  &       35.87  &       35.38  &       39.09  &       39.69  \\
									 & VNLB $n_t = 5$ & \best{37.88} & \best{36.01} & \best{35.53} & \best{39.20} & \best{39.74} \\\hline
%									                                                                                           
		\multirow{5}{*}{$20$} & V-BM4D-np      &       32.91  &       31.50  &       30.94  &       33.60  &       34.27  \\
		                      & VNLB $n_t = 0$ &       33.77  &       32.44  &       31.68  &       35.61  &       35.60  \\
									 & VNLB $n_t = 3$ &       34.45  &       32.90  &       32.15  &       35.89  &       36.12  \\
									 & VNLB $n_t = 5$ & \best{34.59} & \best{33.02} & \best{32.27} & \best{35.90} & \best{36.12} \\\hline
%									                                                                                           
		\multirow{5}{*}{$40$} & V-BM4D-np      &       30.42  &       29.29  &       28.65  &       31.02  &       31.64  \\
		                      & VNLB $n_t = 0$ &       30.55  &       29.41  &       28.66  &       31.78  &       31.86  \\
									 & VNLB $n_t = 3$ & \best{31.02} & \best{29.73} & \best{29.03} & \best{31.88} & \best{31.92} \\
									 & VNLB $n_t = 5$ & \best{31.06} & \best{29.74} & \best{29.08} &       31.70  &       31.74  \\\hline
	\end{tabular}
	\end{center}
	\caption{PSNRs obtained for the five color sequences from the Middlebury
	dataset \cite{middleburyOflow}. See text for details.}
	\label{tab:psnr}
\end{table}

@@

In this section we present preliminary results obtained with the proposed
method on the classic color test sequences \emph{tennis}, \emph{coastguard}, \emph{foreman},
\emph{bus}. In order to measure the effect of the additional temporal
dimension, we tested our method considering temporal search ranges of $1, 3$ and $5$ frames.
The results are shown in Table \ref{tab:psnr}. The proposed method is labeled VNLB.
For these sequences, the best results were obtained with
$n_t = 5$ (two frames before and after the frame of the current patch). Larger 
values of $n_t$ do not necessarily lead to better results. One possible reason
for that is that our search does not take motion into account. As a
consequence, in the presence of motion, similar patches might exit of the
search range after a certain number of frames.

For comparison, we also show the result of V-BM3D and two versions of V-BM4D.
The method labeled V-BM4D-\cite{Maggioni2012} corresponds to the results reported
in \cite{Maggioni2012}. The result labeled V-BM4D-np was obtained using the implementation
available online \cite{bm4dcode}. This implementation provides three parameter
profiles of increasing quality and complexity: ``low complexity profile'', ``normal
profile'' and ``modified profile''. The results shown here were obtained with the
``normal profile'' which is the default. We have included this result, because
it has a computation time comparable to the one of our method. Running with a
single core in a Intel Xeon X7560 (2.27GHz) CPU, 
our current implementation takes on average $9s$ per frame. V-BM4D takes $12s$
per frame with the normal profile and three times more with the modified profile.

@@

We also show quantitative results obtained in for some sequences from the
optical flow Middlebury dataset (the sequences have 8 frames each), and compare
agaist V-BM4D-np. For these sequences, the proposed method outpeforms V-BM4D-np.

>>>>

\begin{table}[htp!]
	\begin{center}
	\renewcommand{\tabcolsep}{3mm}
	\renewcommand{\arraystretch}{1.0}
	\begin{tabular}{ c | l |c c c c}
		\hline
		\rule{0pt}{12pt}$\sigma$ & Method                  & Tennis       & Coastguard   & Foreman      & Bus          \\\hline
		\multirow{5}{*}{$10$} & V-BM4D \cite{Maggioni2012} & \best{36.42} & \best{37.27} &       37.92  &       36.23  \\
		                      & V-BM4D-mp                  &       35.90  &       36.30  &       37.21  &       35.38  \\
		                      & V-BM4D-np                  &       35.56  &       36.20  &       36.90  &       35.09  \\
		                      & V-BM3D                     &       36.04  &       36.82  &       37.52  &       34.96  \\
		                      & VNLB $n_t = 0$             &       34.43  &       36.70  &       37.21  &       35.58  \\
		                      & VNLB $n_t = 3$             &       35.04  &       37.19  &       37.88  &       36.19  \\
									 & VNLB $n_t = 5$             &       35.28  & \best{37.30} & \best{38.11} & \best{36.37} \\\hline
%									 
		\multirow{5}{*}{$20$} & V-BM4D \cite{Maggioni2012} & \best{32.88} & \best{33.61} & \best{34.62} & \best{32.27} \\
		                      & V-BM4D-mp                  &       31.98  &       32.44  &       33.70  &       31.34  \\
		                      & V-BM4D-np                  &       31.67  &       32.24  &       33.34  &       30.95  \\
		                      & V-BM3D                     &       32.54  &       33.39  &       34.49  &       31.03  \\
		                      & VNLB $n_t = 0$             &       30.65  &       32.70  &       33.64  &       31.39  \\
									 & VNLB $n_t = 3$             &       31.26  &       33.35  &       34.25  &       32.11  \\
									 & VNLB $n_t = 5$             &       31.49  & \best{33.55} &       34.45  & \best{32.35} \\\hline
%									 
		\multirow{5}{*}{$40$} & V-BM4D \cite{Maggioni2012} & \best{29.52} & \best{30.00} & \best{31.30} &       28.32  \\
		                      & V-BM4D-mp                  &       28.14  &       28.73  &       30.09  &       27.44  \\
		                      & V-BM4D-np                  &       27.97  &       28.43  &       29.69  &       27.02  \\
									 & V-BM3D                     &       29.20  & \best{29.99} &       31.17  &       27.34  \\
		                      & VNLB $n_t = 0$             &       27.43  &       28.88  &       30.15  &       27.60  \\
									 & VNLB $n_t = 3$             &       27.97  &       29.60  &       30.72  &       28.23  \\
									 & VNLB $n_t = 5$             &       28.11  &       29.78  &       30.82  & \best{28.40} \\\hline
	\end{tabular}
	\end{center}
	\caption{PSNRs obtained for the four classic color test sequences used in
	\cite{Maggioni2012}. See text for details.}
	\label{tab:psnr-classic}
\end{table}

\begin{table}[htp!]
	\begin{center}
	\renewcommand{\tabcolsep}{2mm}
	\renewcommand{\arraystretch}{1.0}
	\begin{tabular}{ c | l |c c c c c}
		\hline
		\rule{0pt}{12pt}$\sigma$ & Method     & Army & DogDance & Evergreen & Mequon & Walking  \\\hline
		\multirow{5}{*}{$10$} & V-BM4D-np      &       37.77  &       35.70  &       35.40  &       38.09  &       38.85  \\
		                      & VNLB $n_t = 0$ &       36.90  &       35.42  &       34.84  &       38.43  &       38.86  \\
		                      & VNLB $n_t = 3$ &       37.65  &       35.87  &       35.38  &       39.09  &       39.69  \\
									 & VNLB $n_t = 5$ & \best{37.88} & \best{36.01} & \best{35.53} & \best{39.20} & \best{39.74} \\\hline
%									                                                                                           
		\multirow{5}{*}{$20$} & V-BM4D-np      &       32.91  &       31.50  &       30.94  &       33.60  &       34.27  \\
		                      & VNLB $n_t = 0$ &       33.77  &       32.44  &       31.68  &       35.61  &       35.60  \\
									 & VNLB $n_t = 3$ &       34.45  &       32.90  &       32.15  &       35.89  &       36.12  \\
									 & VNLB $n_t = 5$ & \best{34.59} & \best{33.02} & \best{32.27} & \best{35.90} & \best{36.12} \\\hline
%									                                                                                           
		\multirow{5}{*}{$40$} & V-BM4D-np      &       30.42  &       29.29  &       28.65  &       31.02  &       31.64  \\
		                      & VNLB $n_t = 0$ &       30.55  &       29.41  &       28.66  &       31.78  &       31.86  \\
									 & VNLB $n_t = 3$ & \best{31.02} & \best{29.73} & \best{29.03} & \best{31.88} & \best{31.92} \\
									 & VNLB $n_t = 5$ & \best{31.06} & \best{29.74} & \best{29.08} &       31.70  &       31.74  \\\hline
	\end{tabular}
	\end{center}
	\caption{PSNRs obtained for the five color sequences from the Middlebury
	dataset \cite{middleburyOflow}. See text for details.}
	\label{tab:psnr-middlebury}
\end{table}

@@

In this section we present preliminary results obtained with the proposed
method on the classic color test sequences \emph{tennis}, \emph{coastguard}, \emph{foreman},
\emph{bus}. In order to measure the effect of the additional temporal
dimension, we tested our method considering temporal search ranges of $1, 3$ and $5$ frames.
The results are shown in Table \ref{tab:psnr-classic}. The proposed method is labeled VNLB.
For these sequences, the best results were obtained with
$n_t = 5$ (two frames before and after the frame of the current patch). Larger 
values of $n_t$ do not necessarily lead to better results. One possible reason
for that is that our search does not take motion into account. As a
consequence, in the presence of motion, similar patches might exit of the
search range after a certain number of frames.

For comparison, we also show the result of V-BM3D and three versions of V-BM4D.
The method labeled V-BM4D-\cite{Maggioni2012} corresponds to the results reported
in \cite{Maggioni2012}. The results labeled V-BM4D-np and V-BM4D-mp were
obtained using the implementation available online \cite{bm4dcode}. This
implementation provides three parameter profiles of increasing quality and
complexity: ``low complexity profile'', ``normal profile'' and ``modified
profile''. We show the results obtained with the normal (V-BM4D-np) and
modified (V-BM4D-mp) profiles.
Let us note that the normal profile has a
computation time comparable to our method. Running with a
single core in a Intel Xeon X7560 (2.27GHz) CPU, 
our current implementation takes on average $10s$ per frame for a video of CIF
resolution ($352\times288$). V-BM4D takes $13s$ per frame with the normal
profile and $44s$ with the modified profile.

@@

We also show quantitative results obtained in for some sequences from the
optical flow Middlebury dataset (the sequences have 8 frames each), and compare
agaist V-BM4D-np (see table \ref{tab:psnr-middlebury}. For these sequences, the
proposed method outpeforms V-BM4D-np.

### 2016-07-20 doc/201504_vnlbayes_workplan/workplan.tex

\usepackage[english,activeacute]{babel}
\usepackage[english]{layout}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage[dvips]{graphicx}
\usepackage{color}
\usepackage{subfig}
\usepackage{colonequals}
\usepackage[latin1]{inputenc}
\usepackage{url}
\usepackage{epsfig}
%\usepackage{dsfont}

@@

\usepackage[left=1.2in,right=1.2in]{geometry}

@@

% NOTE: COMMENT !!
\newcommand{\mathds}[1]{\mathbb{#1}}

@@

\title{Video denoising with non-local means}
\author{}
\date{}

@@

\maketitle
\abstract{Brief description of an extension of the non-local
means algorithm to video denoising.}

\section*{Overview}

This implementation of non-local means comes from modifying the non-local Bayes
algorithm. The only difference is that groups patches are denoised via averages
weighted by similarity, instead of the empirical Bayes estimate of non-local Bayes.

The code in Listing \ref{src:main-overview} shows an overview of the the
algorithm. The first step computes an initial basic estimate which is used as an
oracle for the second step. In the second step, the basic estimate is used
to compute patch distances and similarity weights. We now provide some details
about both steps:

\section*{Step 1: basic estimate}

\paragraph{Patch distances:} The video is converted to YUV colorspace, and only
the Y component is used for the computation of distances and similarity
weights.

\paragraph{Search for similar patches:} We search for similar patches of size
$s_1\times s_1$ in a spatio-temporal window of size $W_{x,1}\times W_{x,1}\times
W_{t,1}$ centered around the current pixel $x = (x_0, x_1, t)$. From all
patches in the search window, we keep only
the $N_{\text{sim},1}$ most similar. This set of patches is the output of the
patch search stage. We denoted it by $\mathcal G_x$, and call it \verb+group+
in the pseudo-code.

\paragraph{Non-local means estimate:} The group of $N_{\text{sim},1}$ patches
is denoised via similarity weighted averages. Consider a noisy patch $\hat p_y\in \mathcal
G_x$. Then its non-local means estimate is given by
\[p_y^{\text{NLM},1} = \frac1{C(\hat p_y; \mathcal G_x)}\sum_{\hat p_z\in\mathcal G_x} w(\hat p_y, \hat p_z)\hat p_z,\]
where $w(\hat p_y, \hat p_z)$ is the similarity weight between patches $\hat
p_y$ and $\hat p_z$ and $C(\hat p_y; \mathcal G_x)$ is a normalization
constant, and the similarity is computed following BUADESIPOL:
\[w(\hat p_y, \hat p_z) = \exp\left(-\frac1{h_1^2}\max(\|\hat p_y - \hat p_z\|_Y^2, 2\sigma^2/3)\right),\]
where $\|\,\cdot\,\|_Y$ is the Euclidean norm of the Y component. The factor
$1/3$ in the above formula is because we are working with the $Y$
component.

\paragraph{Aggregation:} The estimated pathes of $\mathcal G_x$
are aggregated into their original positions. The result of this aggregation is
the output of the first step: the \emph{basic estimate}. The positions of these
patches are labeled as processed. Optionally to reduce computations, we can label
their 4 spatial neighbors as being also processed, as in NL-Bayes.

\section*{Step 2: final estimate}

\paragraph{Search for similar patches:} Patches are of size
$s_2\times s_2$, and the search is performed in a spatio-temporal window of
size $W_{x,2}\times W_{x,2}\times W_{t,2}$ centered around the current pixel $x
= (x_0, x_1, t)$. In the second stage, the distance between patches is computed
using the RGB components of the basic estimate. Two sets of patches are built,
taking patches from the basic estimate in $\mathcal G^b_x$ and their noisy versions
in $\mathcal G_x^n$.

The number of similar patches kept is adaptive. Let $d_{N_{\text{sim},2}}$
be the distance between the reference patch and its $N_{\text{sim},2}$ most similar patch.
All patches with a distance
to the reference patch smaller than $\max(\tau_2, d_{N_{\text{sim},2}})$ are kept.
Thus, $N_{\text{sim},2}$ is a lower bound on the number of similar patches.

\paragraph{Non-local means estimate:} As in step 1, the group $\mathcal G_x^n$ of patches
is denoised via similarity weighted averages. The similarity weight is computed
from the corresponding patches in $\mathcal G_x^b$. Thus, for a noisy patch
$\hat p_y\in \mathcal
G_x^n$, we have:
\[p_y^{\text{NLM},2} = \frac1{C(p^b_y; \mathcal G^b_x)}\sum_{\hat p_z\in\mathcal G^n_x} w(p^b_y, p^b_z)\hat p_z.\]
The similarity $w(\hat p_y, \hat p_z)$ is computed as in step 1, but using the
RGB components:
\[w(p^b_y, p^b_z) = \exp\left(-\frac1{h_2^2}\max(\|p^b_y - p^b_z\|_{\text{RGB}}^2, 2\sigma^2)\right).\]

\paragraph{Aggregation:} As in step 1.

\begin{lstlisting}[%
	float=h,
	caption={Overview of main function},
	label=src:main-overview,
	xleftmargin=.9cm,
	xrightmargin=.9cm]
function final_vid = videoNLMeans(noisy_vid, params1, params2)

%%%%%%%%
% step 1
%%%%%%%%

% convert to YUV colorspace
noisy_vid = convertRGBtoYUV(noisy_vid);

% label all pixels as non-processed
processed = Video(width, height, nframes, false);

% initialize basic estimate as zero
basic_vid = Video(width, height, nframes, channels, 0);

% process video
for x = 1:noisy_vid.nPixels,
	if processed(x) == false,
		% search for similar patches around the reference one
		group = getSimilarPatchesStep1(noisy_vid, x, params1);

		% denoise patches in group via similarity-weighted averages
		group = nlMeansEstimateStep1(group, params1);

		% aggregate group over basic estimate. update processed pixels
		[basic_vid, processed] = aggregateStep1(basic_vid, processed, group, params1);
	end
end

% convert back to RGB colorspace
noisy_vid = convertYUVtoRGB(noisy_vid);
basic_vid = convertYUVtoRGB(basic_vid);

%%%%%%%%
% step 2
%%%%%%%%

% label all pixels as non-processed
processed = Video(width, height, nframes, false);

% initialize final estimate as zero
final_vid = Video(width, height, nframes, channels, 0);

% process video
for x = 1:noisy_vid.nPixels,
	if processed(x) == false,
		% search for similar patches around the reference one
		[group_noisy, group_basic] = getSimilarPatchesStep2(noisy_vid, basic_vid, x, params2);

		% denoise patches in group via similarity-weighted averages
		group_basic = nlMeansEstimateStep2(group_noisy, group_basic, params2);

		% aggregate group estimate, and update mask of processed pixels
		[final_vid, processed] = aggregateStep2(final_vid, processed, group, params2);
	end
end
\end{lstlisting}

\section*{Parameters}

Parameters used in the patch search: $W_{x,i}, W_{t,i}, N_{\text{sim},i}$ and
$\tau_2$, are computed as a function of $\sigma$, following the empirical rules
provided in LEBRUNIPOL.

Parameters $s_1$ and $h_1$ are computed as a function of $\sigma/\sqrt{3}$ following 
the empirical rules provided in BUADESIPOL for color images. In principle,
the parameters for grayscale images of BUADESIPOL should be better since weights are
computed based on the Y component, but performed worse on the Middleburry
sequences.

Parameters $s_2$ and $h_2$ were set by trial and error.

>>>>

\usepackage[english,activeacute]{babel}
\usepackage[english]{layout}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage[dvips]{graphicx}
\usepackage{color}
\usepackage{subfig}
\usepackage{colonequals}
\usepackage[latin1]{inputenc}
\usepackage{url}
\usepackage{epsfig}
\usepackage{dsfont}

@@

%\usepackage[left=1.2in,right=1.2in]{geometry}

@@

@@

\title{Temporal consistency in Video NL-Bayes}
\author{}
\date{}

@@

\maketitle
\abstract{Strategies for achieving temporal consistency in video
NL-Bayes using 2D patches.}

\subsection*{Overview}

NL-Bayes groups similar 2D patches and denoise them jointly with a
Wiener shrinkage operator, by assuming that the prior distribution of
the noiseless group is Gaussian. This approach is able to achieve
high PSNRs, however
\begin{enumerate}
	\item for high noise power the results lack temporal consistency,
		and
	\item it is computationally costly.
\end{enumerate}

In order to tackle both issues, we will try to use motion
information. First to achieve temporal consistent results, and
second to speed-up the search for similar patches by searching
in a smaller area around the motion trajectory.
%
In a first stage, we will forget about the computational cost, and
focus on achieving high quality, temporal consistent results.

\bigskip

\bigskip

\begin{figure}[htpb!]
	\centering
	\includegraphics[width=0.33\textwidth]{figs/approach1}%
	\includegraphics[width=0.33\textwidth]{figs/approach2}%
	\includegraphics[width=0.33\textwidth]{figs/approach3}
	\caption{Diagrams of three approaches for a 1D video. Motion
	trajectories are represented by the gray doted lines. Patches
	in the patch group for pixel $(x,t)$ are shown as vertical bars.
   From left to right, A1, A2 and A3.}
	\label{fig:3_approaches}
\end{figure}

We propose four strategies. The difference is on how we build the patch 
group $G(x,t)$ of patches similar to the one on $(x,t)$.
By testing these approaches we should evaluate if we can impose temporal 
consistency by manipulating the set of similar patches, which seems to 
be the simplest approach. 
\begin{enumerate}
	\item[\textbf{A0.}] $G(x,t)$ is built by considering similar
		patches in a spatio-temporal region centered at the motion
		trajectory through $(x,t)$. 
	\item[\textbf{A1.}] $G(x,t)$ is built by considering patches in the motion trajectory
		through $(x,t)$. This approach only exploits temporal redundancy. The amount
		of noise reduction will be bounded by the length of the trajectories.
	\item[\textbf{A2.}] $G(x,t)$ is build from the motion trajectory through $(x,t)$,
		plus some similar patches which are not require to lie on the motion
		trajectory.
	\item[\textbf{A3.}] $G(x,t)$ is build from the motion trajectory through $(x,t)$,
		plus some similar patches which are not require to lie on the motion
		trajectory, toghether with their motion trajectory.
\end{enumerate}

\bigskip

\bigskip

\subsection*{Motion estimation and its reliability}

All the previous approaches rely on an estimate of the motion. Computing a 
reliable motion estimate in the presence of noise is itself a problem.
to compute in the presence of high noise.

We will start by testing optical flow algorithms. We should identify 
algorithms that are less sensitive to noise. Also, we can use some tricks
to reduce the noise level:
\begin{enumerate}
	\item Estimate motion on a zoomed-out version of the image (as a side
		effect, this is good for computational cost)
	\item Apply a temporal filter. If the motion is uniform (no acceleration)
		temporal filtering conmutes with the warping induced by the motion, thus
		corresponding pixels can still be matched. For a short-time temporal
		filter we could gain some noise reduction for motions that have a small
		acceleration. 
	\item Other\dots ?
\end{enumerate}

\bigskip

\bigskip

\subsection*{Work plan}

\begin{enumerate}
	\item Evaluate different optical flow algorithms and their
		robustness to noise. Evaluate the effect of zooming the image
		out and temporal smoothing.
	\item Implement and test approach A0.
	\item Implement and test approach A1.
	\item Implement and test approach A2.
	\item Implement and test approach A3.
\end{enumerate}
